Synthesizing Quotient Lenses

### 2018-03-13 papers/QuotientLenses/main.tex
add correctness proof

@@

\bcp{Some of the citations need some love---e.g., the first one.}
\bibliographystyle{plain}
\bibliography{local}

>>>>

\bcp{Some of the citations need some love---e.g., the first one.}

\bibliographystyle{plain}
\bibliography{local}

@@

\section{Proof of Correctness of \textproc{SynthQRELens}}
Theorem~\ref{thm:alg-correct} states that
  Given QREs $Q_1$ and $Q_2$, and a set of examples
  $\{(x_1,y_1),\ldots,(x_n,y_n)\}$, if there is a QRE lens $q : Q_1
  \Leftrightarrow Q_2$ such that $q.\get(x_i) \equiv_{Q_2} y_i \text{ and }
q.\lput(y_i) \equiv_{Q_1} x_i$, then $\textproc{SynthQRELens}(Q_1,Q_2,exs)$ will
return such a lens.  We prove that here.

\begin{lemma}[Algorithm Soundness]
  If $q = \textproc{SynthQRELens}(Q_1,Q_2,exs)$, then $q : Q_1 \Leftrightarrow
  Q_2$ and $q.\get(x_i) \equiv_{Q_2} y_i$  and 
$q.\lput(y_i) \equiv_{Q_1} x_i$ for all $(x_i,y_i)\in exs$.
\end{lemma}
\begin{proof}
  As $q = \textproc{SynthQRELens}(Q_1,Q_2,exs)$, we know that $q =
  \rquot(\lquot(Q_1, \ell), Q_2)$. Furthermore, we know that $\ell =
  \Call{SynthBijectiveLens}{R_1,R_2,exs'}$, where $exs' = \Call{Map}{exs,fun \,
    (ex_l,ex_r) \to (\canonize(Q_1)(ex_l),\canonize(Q_2)(ex_r))}$. By the correctness of
  $\textproc{SynthBijectiveLens}$, we know that $\ell.\get(x_i') = y_i'$ and
  $\ell.\lput(y_i') = x_i'$ for all $(x_i',y_i')\in exs'$. By definitions of
  $\rquot$ and $\lquot$, this means that:\\
$\rquot(\lquot(Q_1, \ell),
  Q_2).\get(x_i)$\\
 = $\ell.get(\canonize(Q_1)(x_i))$\\ $= \ell.get(x_i') = y_i' =
  \canonize(Q_2)(y_i) \equiv_{Q_2} y_i$ and\\
\\
$\rquot(\lquot(Q_1, \ell),
  Q_2).\lput(y_i)$\\
 = $\ell.\lput(\canonize(Q_2)(y_i))$\\ $= \ell.\lput(y_i') = x_i' =
  \canonize(Q_1)(x_i) \equiv_{Q_1} x_i$ as desired.
\end{proof}

\begin{lemma}[Algorithm Completeness]
  If there exists a QRE lens $q : Q_1 \Leftrightarrow Q_2$ such that
  $q.\get(x_i) \equiv_{Q_2} y_i$ and $q.\lput(y_i) \equiv_{Q_1} x_i$ for all
  $(x_i,y_i)\in exs$, then $\textproc{SynthQRELens}(Q_1,Q_2,exs)$ terminates.
\end{lemma}
\begin{proof}
  By Theorem~\ref{normal form}, there exists a bijective lens $\ell : K(Q_1)
  \Leftrightarrow K(Q_2)$, such that $q' = \rquot(\lquot(Q_1, \ell), Q_2)$ is
  semantically equal to $q$.

  This means that $q'.\get(x_i) \equiv_{Q_2} y_i$ and $q'.\lput(y_i)
  \equiv_{Q_1} x_i$ for all $(x_i,y_i)\in exs$. Unfolding the definitions of
  $\rquot$ and $\lquot$, we get:\\
  $q'.\get(x_i) = \ell.\get(\canonize(Q_1)(x_i)) = \canonize(Q_2)(y_i)$ and\\
  $q'.\lput(y_i) = \ell.\lput(\canonize(Q_2)(y_i)) = \canonize(Q_1)(x_i)$ for all
  $(x_i,y_i)\in exs$.

  By correctness of $\textproc{SynthBijectiveLens}$, we know that
  $\Call{SynthBijectiveLens}{R_1,R_2,exs'}$ terminates, so the entire algorithm
  terminates. 
\end{proof}

With soundness and completeness, we trivially get the correctness theorem.
